A free/open-source Kazakh-Tatar machine translation system

### 2013-04-20 paper/paper.tex
minor
a little work on bilingual lexicon section

% FIXME: the following sh... stuff needs to be rephrased
The bilingual lexicon currently contains 9,269 stem to stem correspondences and was build mostly by hand (translating Kazakh stems unrecognized by the morphological analyzer into Tatar). Part of toponyms and other proper names was translated semi-automatically looking up in Wikipedia links (also some of the Russian loanwords were the result of intersection of Russian and Kazakh wordlists - such as "автомобиль", "гонорар" etc).

@@

The grammar currently has only four rules, but given the closeness of the languages, the 
majority of ambiguity may be passed through from one language to the other.

>>>>

% FIXME: the following sh... stuff needs to be rephrased
The bilingual lexicon currently contains 9,269 stem-to-stem correspondences and was built mostly by hand (i.e., by translating Kazakh stems unrecognized by the morphological analyzer into Tatar).  Some toponyms and other proper names were translated semi-automatically by looking up links in Wikipedia; also, some Russian loanwords common to both languages (such as "автомобиль", "гонорар" etc) were added to the bilingual dictionary automatically by taking the intersection of Russian and Kazakh wordlists.

@@

The grammar currently has fifty-eight rules.
%but given the closeness of the languages, the 
%majority of ambiguity may be passed through from one language to the other.
